\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-23 WOOT/Files/related_work.tex
resolve the problem of table in related work

		\hline
		\diagbox {Defence}{Attack} & Rubbery Ducky\cite{rubber}, \cite{rubberducky2020},USBderivery\cite{usbdriver} & Duqu\cite{duqu} & JFC\cite{JFCImpact}&\cite{smartphone}\cite{poweremi} and \cite{usbdriver}& Armory\\

>>>>

		\hline
		\diagbox[width=1.46in] {Defence}{Attack} & Rubbery Ducky\cite{rubber}, \cite{rubberducky2020},USBderivery\cite{usbdriver} & Duqu\cite{duqu} & JFC\cite{JFCImpact}&\cite{smartphone}\cite{poweremi} and \cite{usbdriver}& Armory\\
